\documentclass[10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage{helvet} % Default font is the helvetica postscript font
\usepackage{hyperref}
\usepackage{etaremune}
\usepackage{multicol}

\newsectionwidth{0pt} % Stops section indenting


\begin{document}

\name{Dr. Vincent A. Knight\\ \\} % Your name at the top

% If you don't want one of the addresses, simply remove all the text in the first or second \address{} bracket

\address{{\bf Cardiff University} \\ School of Mathematics \\ Senghennydd Road \\ Cardiff, CF24 4AG \\ (+44) 29 2087 5548} % Your address 1

\address{\hfill{\href{http://www.vknight.org}{www.vknight.org}}\\ \hfill{G+: \href{https://plus.google.com/+VincentKnight/posts}{+Vincent Knight}}\\ \hfill{twitter: \href{https://twitter.com/drvinceknight}{@drvinceknight}}\\ \hfill{github: \href{https://github.com/drvinceknight}{drvinceknight}}\\\hfill{blog: \href{http://drvinceknight.blogspot.co.uk/}{Un peu de math}}} % Your address 2

\begin{resume}

\vspace{1cm} % Gap between title and text

\begin{multicols}{2}
\begin{itemize}
    \item {\sl Senior lecturer}

    \item {\sl Deputy director of engagement}

    \item {\sl Sustainable Software Institute Fellow}

    \item {\sl Chair of OR in Schools}

    \item {\sl Area editor for Health Systems}

    \item {\sl Phoenix project advisory board}

    \item {\sl Cardiff Python user group meetup organiser}

    \item {\sl PyCon UK organising committee}

\end{itemize}
\end{multicols}

\section{\centerline{AWARDS}}

\vspace{1cm} % Gap between title and text

\begin{itemize}
    \item {\sl 2016: School of Mathematics student award for best lecturer}

    \item {\sl 2015: Times higher education award for modelling unit}

    \item {\sl 2014: Cardiff University Recognising Excellence rising star award}

    \item {\sl 2005: School of Mathematics award: graduated first in my year}

\end{itemize}

\section{\centerline{RESEARCH INTERESTS}}

\vspace{1cm} % Gap between title and text

\begin{itemize}
    \item {\sl Game Theory: Strategic behaviour in queues and the Iterated Prisoner's dilemma}

    \item {\sl Markov modelling: Queueing processes and evolutionary dynamics}

    \item {\sl Healthcare: Applied modelling of patient flow}

    \item {\sl Pedagogy: Active learning approaches}

\end{itemize}

\section{\centerline{APPOINTMENTS}}

\vspace{8pt}

\sl{Senior Lecturer}  \hfill 2016 -
present\\
Cardiff University\\

\sl{Lecturer}  \hfill 2011 -
2016\\
Cardiff University\\

\sl{Post Doctoral Researcher}  \hfill 2009 -
2011\\
Cardiff University\\

\section{\centerline{ACADEMIC QUALIFICATIONS}}

\vspace{8pt} % Gap between title and text

{\sl Postgraduate Certificate in University Teaching and Learning},\\
\textbf{Obtained with distinction}\\
Cardiff University\hfill 2013

{\sl Ph.D. in Enumerative Combinatorics},\\
\textbf{Alternating Sign Matrix Polytopes}\\
Cardiff University\hfill 2009

{\sl B.Sc. (Hons) Mathematics},\\
\textbf{Graduated top of my class}\\
Cardiff University\hfill 2005

{\sl Baccalaureat Scientifique},\\
\textbf{Fluent in French}\\
Lycee du Pre Saint Sauver, St Claude, Jura, France\hfill 2002

\section{\centerline{PUBLICATIONS}}

\vspace{12pt} % Gap between title and text

\begin{etaremune}
\item
2016: \textbf{Ambulance Allocations for Maximising Survival within a Heterogeneous Population using a Heterogeneous Fleet.}\\
Leanne Smith, Paul Harper, Vincent Knight
\\
\textbf{Submitted to the journal of the operational research society.}
\\

\item
2016: \textbf{Measuring the Price of Anarchy in Critical Care Unit Interactions.}\\
Knight VA., Komenda I, Griffiths J.
\\
\textbf{Accepted in the journal of the operational research society.}
\\

\item
2016: \textbf{Editorial: Operations Research for Health Care ESI XXXI — OR applied to Health in a Modern World.}\\
Aringhieri, R., Knight, V., Smith, H.
\\
\textbf{Health Systems}
\\

\item
2016: \textbf{Virtual Machine Warmup Blows Hot and Cold}\\
Barrett, E., Bolz, C. F., Killick, R., Knight, V., Mount, S., Tratt, L.
\\
\url{http://arxiv.org/abs/1602.00602}
\\

\item
2016: \textbf{Editorial: Operations Research for Health Care ESI XXXI — OR applied to Health in a Modern World.}\\
Aringhieri, R., Knight, V., Smith, H.
\\
\textbf{Operations Research for Health Care, 8, 22–23.}
\\
\url{http://doi.org/10.1016/j.orhc.2016.01.002}
\\

\item
2016: \textbf{An Open Framework for the Reproducible Study of the Iterated Prisoner’s Dilemma.}\\
Vincent Knight, Owen Campbell, Marc Harper, Karol Langner, James Campbell, Thomas Campbell, Alex Carney, Martin Chorley, Cameron Davidson-Pilon, Kristian Glass, Nikoleta Glynatsi, Tomáš Ehrlich, Martin Jones, Georgios Koutsovoulos, Holly Tibble, Jochen Müller, Geraint Palmer, Piotr Petunov, Paul Slavin, Timothy Standen, Luis Visintini, Karl Molden.
\\
\textbf{Journal of open research software.}
\\
\url{http://openresearchsoftware.metajnl.com/article/10.5334/jors.125/}
\\

\item
2016: \textbf{Time-dependent stochastic methods for managing and scheduling Emergency Medical Services}\\
J.L. Vile, J.W. Gillard, P.R. Harper, V.A. Knight.
\\
\textbf{Operations Research for Health Care.}
\\
\url{http://www.sciencedirect.com/science/article/pii/S2211692314200518}
\\

\item
2015: \textbf{Containment of socially optimal policies in multiple-facility Markovian queueing systems.}\\
Rob Shone, Vincent Knight, Paul Harper, Janet Williams, John Minty
\\
\textbf{Journal of the Operational Research Society.}
\\
\url{http://link.springer.com/article/10.1057/jors.2015.98}
\\

\item
2015: \textbf{Playing games: a case study in active learning applied to Game Theory.}\\
Vince Knight
\\
\textbf{Connections}
\\
\url{https://journals.gre.ac.uk/index.php/msor/article/view/254}
\\

\item
2015: \textbf{Compliance with National Guidelines for Stroke in Radiology.}\\
Izabella Komenda, Hannah Williams, Vincent Knight
\\
\textbf{Operations Research for Health Care.}
\\
\url{http://www.sciencedirect.com/science/article/pii/S2211692314200191}
\\

\item
2015: \textbf{Modelling of psoriasis patient flows for the reconfiguration of secondary care services and treatments}\\
Kayne Putman, Alex Anstey, Paul R Harper, Vince A Knight
\\
\textbf{Health Systems.}
\\

\item
2015: \textbf{Rostering staff at a mathematics support service using a finite-source queueing model}\\
Gillard J., Knight V., Vile J., Wilson R.
\\
\textbf{IMA Journal of Management Mathematics. 27 (2)}
\\

\item
2014: \textbf{Mathematical modelling of patient flows to predict critical care capacity required following the merger of two district general hospitals into one}\\
J. Williams, S. Dumont, J. Parry-Jones, I. Komenda, J. Griffiths, V. Knight
\\
\textbf{Anaesthesia. 70 (1)}
\\

\item
2014: \textbf{Operational research ambassadors in schools}\\
Bradshaw N.A., Harper P, Knight V., Orpin L.
\\
\textbf{Proceedings of the HEA STEM, Edinburgh 2014}
\\

\item
2014: \textbf{Tweeting the Terror: Modelling the Social Media Reaction to the Woolwich Terrorist Attack}\\
Burnap P, Williams ML, Sloan L, Rana O, Housley W, Edwards A, Knight V, Procter R., Voss A. (
\\
\textbf{Social Network Analysis and Mining}
\\

\item
2014: \textbf{Mathematical modelling of patient flows to predict critical care capacity required following the merger of two district general hospitals into one.}\\
J. Williams, S. Dumont, J. Parry-Jones, I. Komenda, J. Griffiths, V. Knight.
\\
\textbf{Anaesthesia. 70 (1)}
\\

\item
2013: \textbf{Selfish routing in public services.}\\
Knight VA, Harper PR.
\\
\textbf{European Journal of Operational Research. 230 (1) 122-132}
\\

\item
2013: \textbf{Using Singular Spectrum Analysis to Obtain Staffing Level Requirements in Healthcare.}\\
Knight VA, Gillard J
\\
\textbf{Journal of the Operational Research Society}
\\

\item
2013: \textbf{Comparisons between observable and unobservable M/M/1 queues with respect to optimal customer behavior}\\
Shone R, Knight VA, Williams JE
\\
\textbf{European Journal of Operational Research}
\\

\item
2012: \textbf{Ambulance Allocation for Maximal Survival with Heterogeneous Outcome Measures.}\\
Knight VA, Harper PR, Smith L
\\
\textbf{OMEGA - The International Journal of Management Science. 40 (6) 918--926}
\\

\item
2012: \textbf{How Efficient can an Emergency Unit be? A Perfect World Model.}\\
Baboolal K, Griffiths J, Knight VA, Nelson AV, Voake C, Williams JE.
\\
\textbf{Emergency Medicine Journal.}
\\

\item
2012: \textbf{Discrete Conditional Phase-Type Models Utilising Classification Trees: Application to Modelling Health Service Capacities.}\\
Harper PR, Knight VA, Marshall A.
\\
\textbf{European Journal of Operational Research. 219 (3) 522--530}
\\

\item
2012: \textbf{Modelling Emergency Medical Services with Phase Type Distributions.}\\
Knight VA, Harper PR.
\\
\textbf{Health Systems. 1 53-68}
\\

\item
2011: \textbf{On the Peter Principle: An Agent Based Investigation into the Consequential Effects of Social Networks and Behavioural Factors.}\\
Fetta A, Harper PR, Knight VA, Williams JW, Vieira I
\\
\textbf{Physica A: Statistical Mechanics and its Applications.}
\\

\item
2011: \textbf{Forecasting Welsh Ambulance Demand using Singular Spectrum Analysis.}\\
Williams J, Gillard J, Harper PR, Knight VA
\\
\textbf{Journal of the Operational Research Society.}
\\

\item
2011: \textbf{Operational Research Informing National Health Policy}\\
Harper PR, Knight VA, Vieira I, Williams JW
\\
\textbf{Cardiff University. ISBN: 978-0-9569158-0-1}
\\

\item
2011: \textbf{Bed Management in a Critical Care Unit.}\\
Griffiths J, Knight VA, Komenda I.
\\
\textbf{IMA Journal of Management Mathematics.}
\\

\item
2011: \textbf{Modelling Patient Choice in Healthcare Systems: Development and Application of a Discrete Event Simulation with Agent-Based Functionality.}\\
Knight VA, Williams JE, Reynolds I.
\\
\textbf{Journal of Simulation.}
\\

\item
2011: \textbf{Cost-Effective Workforce Planning: Optimising the Dental Team Skill-Mix for England.}\\
Harper PR, Kleinman ER, Gallagher JE, Knight VA
\\
\textbf{Journal of Enterprise Information Management}
\\

\item
2010: \textbf{Forecasting Welsh Ambulance Demand using Singular Spectrum Analysis.}\\
Williams J, Gillard J, Harper PR, Knight VA
\\
\textbf{In Proceedings of the XXXVI International ORAHS Conference}
\\

\item
2008: \textbf{Higher Spin Alternating Sign Matrices}\\
Behrend RE, Knight VA
\\
\textbf{Electronic Journal of Combinatorics.~14(1): R83, 38pp.}
\\

\end{etaremune}

\section{\centerline{RESEARCH STUDENTS}}

\vspace{12pt} % Gap between title and text

\begin{etaremune}
\item
    Nikoleta Glynatsi (PhD) \hfill 2016 -
    present\\
\textbf{Machine learning and the Prisoner's Dilemma}\\

\item
    James Campbell (BSc) \hfill 2016 -
    present\\
\textbf{Fingerprinter prisoner's Dilemma strategies}\\

\item
    Cindy Huang (Nuffield Research Placement) \hfill 2016 -
    2016\\
\textbf{Investigating deadlock in queues with vacation and baulking}\\

\item
    Rhys Ward (Summer) \hfill 2015 -
    2015\\
\textbf{Building Game Theoretical Software in a Research Environment}\\

\item
    James Campbell (Summer) \hfill 2015 -
    2015\\
\textbf{Building Game Theoretical Software in a Research Environment}\\

\item
    Tobenna Peter Igwe (Google Summer of Code) \hfill 2015 -
    2015\\
\textbf{Extending Game Theory in Sage}\\

\item
    Ffinian Sullivan (Nuffield Research Placement) \hfill 2015 -
    2015\\
\textbf{Understanding mixed behaviour in queue balking threshold policies}\\

\item
    Hannah Lorrimore (Summer) \hfill 2015 -
    2015\\
\textbf{Building Game Theoretical Software in a Research Environment}\\

\item
    Geraint Palmer (PhD) \hfill 2014 -
    present\\
\textbf{Jackson networks and healthcare}\\

\item
    Imogen Dunne (BSc.) \hfill 2014 -
    2015\\
\textbf{The Effect of Personality Traits on Academic Achievement in Flipped versus Traditional Learning Environments}\\

\item
    James Campbell (Summer) \hfill 2014 -
    2014\\
\textbf{Building Game Theoretical Software in a Research Environment}\\

\item
    Rhys Jones (BSc.) \hfill 2013 -
    2014\\
\textbf{Modelling Rugby Lineout Strategies Using Game Theory}\\

\item
    Jason Young (MMath) \hfill 2013 -
    2014\\
\textbf{Markov Decision Processes for the study a system of two queues in series.}\\

\item
    Ceri Morse (BSc.) \hfill 2012 -
    2013\\
\textbf{Modelling Lineout Strategies using Game Theory}\\

\item
    Jason Young (Summer) \hfill 2012 -
    2012\\
\textbf{Understanding the effect of selfish behaviour in a series of 2 queues}\\

\item
    Rob Shone (PhD) \hfill 2011 -
    2014\\
\textbf{Individually and Socially Optimal Policies in Queueing Systems with Multiple Heterogeneous Facilities}\\

\item
    Angelico Fetta (PhD) \hfill 2011 -
    2014\\
\textbf{Agent Based Simulation for Complex Health Systems Interventions}\\

\item
    Chappman Sin (BSc.) \hfill 2011 -
    2012\\
\textbf{Mathematical modelling of Risk (the board game)}\\

\item
    Iain Reynolds (Summer) \hfill 2011 -
    2011\\
\textbf{Modelling patient choice in healthcare systems development and application of a discrete event simulation with agent-based functionality}\\

\item
    Izabela Komenda (PhD) \hfill 2010 -
    2013\\
\textbf{Bed management in a critical care unit}\\

\item
    Tatjana Timofejeva (BSc.) \hfill 2010 -
    2011\\
\textbf{Impact of unscheduled care Modelling time varying activities at a Hospital}\\

\item
    Stuart MacGregor (BSc.) \hfill 2010 -
    2011\\
\textbf{A study into two player hide and seek games verifying results from game theory using monte carlo simulation, with a particular application to anti-submarine warfare}\\

\item
    Catherine Fortune (BSc.) \hfill 2010 -
    2011\\
\textbf{Game Theory and the Lemke-Howson algorithm}\\

\item
    Julie Vile (PhD) \hfill 2009 -
    2012\\
\textbf{Time-dependent stochastic modelling for predicting demand and scheduling of emergency medical services}\\

\item
    Fern Gould (BSc.) \hfill 2009 -
    2010\\
\textbf{Game Theory and the Iterated Prisoner's Dilemma}\\

\item
    Tamsin Griffiths (BSc.) \hfill 2009 -
    2010\\
\textbf{Troops to Task Tool and Refugee Estimation}\\

\item
    Leanne Smith (PhD) \hfill 2008 -
    2013\\
\textbf{Modelling emergency medical vehicle services}\\

\end{etaremune}

\section{\centerline{GRANT FUNDING}}

\vspace{12pt} % Gap between title and text

\sl{Sustainable software institute}\\
Fellowship\\
\pounds3,000\hfill{2013 - ongoing}

\sl{Cardiff and Vale University Health Board}\\
Operational Research Modelling to Support Cardiff and Vale UHB\\
\pounds371,427\hfill{2013 - 2018}

\sl{EPSRC}\\
Identifying and modelling victim, business regulatory and malware behaviours in a changing cyberthreat landscape\\
\pounds101,659\hfill{2013 - 2016}

\sl{Aneurin Bevan Health Board}\\
Creation of a Mathematical/OR Modelling Unit to Support the Aneurin Bevan Health Board\\
\pounds319,944\hfill{2013 - 2015}

\sl{ESRC}\\
Hate speech? Understanding the modelling of social media identity formation and behaviour through the Cardiff Online Social Media Observatory (COSMOS)\\
\pounds7,015\hfill{2013 - 2016}

\sl{Health Foundation and Cardiff and Vale University Health Board}\\
Estimating quality improvement and cost reduction for the patient and local health economy of transferring ENT/audiology services into a community setting\\
\pounds61,237\hfill{2013 - 2014}

\sl{LANCS (EPSRC)}\\
Post-Doctoral Training Scheme Grant: Investigating the Effects of Individual Behaviour on Hierarchical queueing Systems\\
\pounds5,000\hfill{2012 - 2012}

\sl{Cardiff University CUROP Award}\\
Developing and Evaluating Mathematical Teaching Resources through Open Source Software\\
\pounds2,200\hfill{2012 - 2012}

\sl{LANCS (EPSRC)}\\
Post-Doctoral Training Scheme Grant: Choice and Healthcare Investigation Project\\
\pounds2,500\hfill{2010 - 2011}

\sl{Cardiff University CUROP Award}\\
Patient Choice: A Discrete Event Simulation\\
\pounds2,500\hfill{2010 - 2012}

\section{\centerline{TEACHING}}

\vspace{12pt} % Gap between title and text

Courses I am currently teaching:

\begin{etaremune}
\item Computing for Mathematics: A course introducing programming to mathematics students.
\item Introduction to Object Oriented Programming: A hackathon introduces students to fundemantal aspects of object oriented prgramming.
\item OR2 - Game Theory: A final year mathematics course covering introductory game theory.
\end{etaremune}

Courses I have taught in the past:

\begin{etaremune}
\item MSc. Week 0: An overview of fundamental mathematics concepts for new MSc students.
\item OR Methods: A course covering: queueing theory, game theory and Markov processes.
\item Introduction to LaTeX: A brief introduction to LaTeX.
\item Advanced Statistical Packages: A course teaching the SAS and R software packages.
\end{etaremune}

\section{\centerline{MEDIA}}

\vspace{12pt} % Gap between title and text


\begin{etaremune}
\item 2016-09-26: Pythagoras' trousers - Election polling

\item 2016-01-27: Namibia broadcasting company - Discussing PyCon Namibia

\item 2015-06-16: BBC Radio Wales - Game Theory and Nash Equilibrium

\item 2015-04-16: Sci screen screening - The Imitation Game

\item 2014-05-05: 2014 Pythagoras Lecture - Mathematics and Healthcare Management

\item 2014-03-19: BBC Parliament - Voice of the Future 2014

\end{etaremune}

\section{\centerline{OUTREACH}}

\vspace{12pt} % Gap between title and text

I participate in a variety of mathematics outreach activities.

\vspace{12pt} % Gap between title and text

\begin{itemize}
\item Monmouth Science initiative.

\item Regular workshops at the School of Mathematics.

\item STEM live: a university wide event.

\item Speaking at the British Science festival 2015.

\end{itemize}

\section{\centerline{SOFTWARE PROJECTS}}

\vspace{12pt} % Gap between title and text

\begin{itemize}
    \item Axelrod: A Python library/github project that replicates Axelrod's tournament.

    \item Nashpy: A Python library to find equilibria in 2 player normal form games

    \item Game Theory in Sage: A collection of code to continue the integration of Game Theoretic capabilities in to Sage.

    \item Virtual Microscope: A web application to display and annotate scanned slides.

    \item ghtalks: Organise and share talks with gh-pages

    \item sklDj: A Django web app interface to machine learning algorithms

    \item Ciw: A Python library for simulation queueing networks

\end{itemize}

\section{\centerline{SOFTWARE COMMUNITY}}

\vspace{12pt} % Gap between title and text

\begin{itemize}
    \item PyDiff: I help organise the Cardiff Pyton user group meetup.

    \item DjangoCon Europe 2015: I was on the organising committee for DjangoCon Europe 2015.

    \item Python Namibia: I help run the Pycon Namibia conference.

    \item PyCon UK: I am on the orgnising committee for PyCon UK.

    \item School of mathematics code club: I help run a code club open to mathematics students.

\end{itemize}

\end{resume}
\end{document}