%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Long Professional Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.latextemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage{helvet} % Default font is the helvetica postscript font
\usepackage{hyperref}
\usepackage{etaremune}
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above

\newsectionwidth{0pt} % Stops section indenting

\begin{document}

%----------------------------------------------------------------------------------------
%	YOUR NAME AND ADDRESS(ES) SECTION
%----------------------------------------------------------------------------------------

\name{Dr. Vincent A. Knight\\ \\} % Your name at the top

% If you don't want one of the addresses, simply remove all the text in the first or second \address{} bracket

\address{{\bf Cardiff University} \\ School of Mathematics \\ Senghennydd Road \\ Cardiff, CF24 4AG \\ (+44) 29 2087 5548} % Your address 1

\address{\hfill{\href{http://www.vincent-knight.com/}{www.vincent-knight.com}}\\ \hfill{G+: \href{https://plus.google.com/+VincentKnight/posts}{+Vincent Knight}}\\ \hfill{twitter: \href{https://twitter.com/drvinceknight}{@drvinceknight}}\\ \hfill{github: \href{https://github.com/drvinceknight}{drvinceknight}}\\\hfill{blog: \href{http://drvinceknight.blogspot.co.uk/}{Un peu de math}}} % Your address 2

%----------------------------------------------------------------------------------------

\begin{resume}

%----------------------------------------------------------------------------------------
%	OBJECTIVE SECTION
%----------------------------------------------------------------------------------------

\section{\centerline{INTRODUCTION}}

\vspace{8pt} % Gap between title and text

Senior lecturer in Operational Research with research interests in Game Theory
and Queueing Theory.
Python programmer with various responsibilities within the python community.
Fellow of the sustainable software institute.

%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{\centerline{APPOINTMENTS}}

\vspace{8pt} % Gap between title and text

{\sl Senior Lecturer} \hfill 2016 - Present \\
School of Mathematics, Cardiff\\

{\sl Lecturer} \hfill 2011 - 2016 \\
School of Mathematics, Cardiff\\

{\sl Post-Doctoral Research Associate} \hfill 2009 - 2011 \\
School of Mathematics, Cardiff\\

%----------------------------------------------------------------------------------------

\vspace{0.2in} % Some whitespace between sections

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{\centerline{ACADEMIC QUALIFICATIONS}}

\vspace{8pt} % Gap between title and text

{\sl Postgraduate Certificate in University Teaching and Learning},\\
\textbf{Obtained with distinction}\\
School of Mathematics, Cardiff \hfill 2013

{\sl Ph.D. in Enumerative Combinatorics},\\
\textbf{``Alternatin Sign Matrices and Polytopes"}\\
School of Mathematics, Cardiff \hfill 2009

{\sl B.Sc. (Hons) Mathematics}, \\
\textbf{Graduated top of my class}\\
School of Mathematics, Cardiff \hfill 2005

{\sl Baccalaur\'{e}at Scientifique},\\
\textbf{Fluent in French},\\
Lyc\'{e}e du Pre Saint Sauver, St Claude, Jura, France \hfill 2002

%----------------------------------------------------------------------------------------

\vspace{0.2in} % Some whitespace between sections


%----------------------------------------------------------------------------------------
% INDICATORS OF ESTEEM
%----------------------------------------------------------------------------------------

\section{\centerline{INDICATORS OF ESTEEM}}

\vspace{8pt} % Gap between title and text

{\sl Research publications within \textbf{high quality} journals.}

{\sl Actively seeking and obtaining research funding.}

{\sl Involvement with various industrial partners.}

{\sl Supervision of multiple PhD students and undergraduate research projects.}

{\sl Elected member of the OR Society General Council, member of the Education and Research Committee, chair of the OR in Schools taskforce and member of the OR Society social media committee.}

{\sl Editorial responsibilities for Health Systems and Operations Research for Health Care.}

{\sl Member of the Phoenix project advisory board.}

%----------------------------------------------------------------------------------------

\vspace{0.2in} % Some whitespace between sections

%----------------------------------------------------------------------------------------
%	RESEARCH INTERESTS
%----------------------------------------------------------------------------------------

\section{\centerline{RESEARCH INTERESTS}}

\vspace{8pt} % Gap between title and text

\begin{itemize}
    \item Game Theory.
    \item Queueing Theory and Simulation.
    \item Healthcare Modelling.
    \item Pedagogy.
\end{itemize}

My main research interests are in the understanding and design of queueing
systems, the iterated prisoners dilemma and pedagogy.

%----------------------------------------------------------------------------------------

\vspace{0.2in} % Some whitespace between sections

%----------------------------------------------------------------------------------------
%   Academic and Professional Activities
%----------------------------------------------------------------------------------------

\section{\centerline{PUBLICATIONS}}

\vspace{-5pt} % Reduce space between section title and contents

\input{publications.tex}

\section{\centerline{ACADEMIC AND PROFESSIONAL ACTIVITIES}}

\vspace{15pt} % Gap between title and text

\begin{center}
\textbf{Teaching:}
\end{center}

\begin{itemize}

\item
 Co organised a 2 week Summer school at the University of Namibia in 2016.

\item
 Designed and delivered two new undergraduate courses: MA1003 ``Computing for Mathematics'' (20 credits) and MA3060 ``OR 2 - Game Theory'' (10 credits).

\item
  Lecturer on the MSc in OR and Applied Statistics / OR, Applied Statistics and Risk programmes, for the modules MAT001 ``OR Methods'' (12 credits) and MAT013 ``Advanced Statistical Packages'' (10 credits). I teach the stochastic methods part of the MAT001 module, namely Decision Trees, Game Theory, Reliability Theory, Inventory Control, Project Management and Queueing Theory. I was responsible for creating new resources (lecture materials, computer workshops, exercise sheets and exam papers) for the new ~MSc modules, 2010/11.

\item
  Teach LaTeX to all research students at the School of Mathematics.
\end{itemize}

\begin{center}
\textbf{Membership of Learned Societies:}
\end{center}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Member of the UK Operational Research Society (since 2009).
\item
  Elected to serve as a member of the Council of the UK Operational Research
  Society, for 6 years from January 2011.
\item
  Member of the ERC (OR Society: Education and Research Committee)
\item
  Chair of ORiS (OR Society: OR in Schools)
\end{itemize}

\begin{center}
\textbf{Editor of Academic Publications:}
\end{center}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Area Editor (Mathematical Modelling) for \href{http://www.palgrave-journals.com/hs/index.html}{Health Systems}.
\item
  Review editor for \href{http://www.elsevier.com/wps/find/journaldescription.cws_home/726198/description\#description}{Operations Research for Health Care}.
\end{itemize}

\begin{center}
\textbf{Reviewer for Academic Publications:}
\end{center}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \href{http://www.palgrave-journals.com/jors/index.html}{Journal of the Operational Research Society}
\item
  \href{http://www.palgrave-journals.com/jos/index.html}{Journal of Simulation}
\item
  \href{http://www.elsevier.com/wps/find/journaldescription.cws_home/300/description\#description}{Computers and OR}
\end{itemize}

\begin{center}
\textbf{Conference Organisation:}
\end{center}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Organised a LANCS one-day workshop on ``Consumer Choice and Healthcare Workshop'', May 2010.
\item
  Member of the Organising Committee of the European Working Group on OR Applied to Health Services (\href{http://www.orahs2011.com}{ORAHS}) Annual Conference, Cardiff, July 2011.
\item
  Healthcare stream organiser for the annual conference of the Operational Research Society:
  \href{http://www.orsoc.org.uk/orshop/(stzuo2ebygs4f145rklamu55)/orcontent.aspx?inc=or52_main.htm}{OR 52}~(2010) and \href{http://www.orsoc.org.uk/orshop/(0gufsl451p5fhmnkztaameeh)/orcontent.aspx?inc=or53_main.htm}{OR53}~(2011).
\item
  Organised two consecutive Python conferences at the University of Namibia
  (2015, 2016).
\item
  Member of the PyCon UK conference committee.
\item
  Co founder and organiser of the Cardiff Python user group.
\end{itemize}


\begin{center}
\textbf{Other}
\end{center}

\begin{itemize}
\item Invited by the House of Commons to judge the mathematics contributions to
    the SET awards 2013, 2014, 2015 and 2016.
\item Core developer of the Axelrod Python library.
\end{itemize}

%----------------------------------------------------------------------------------------

\vspace{0.2in} % Some whitespace between sections

%----------------------------------------------------------------------------------------
%  Grant Funding
%----------------------------------------------------------------------------------------

\section{\centerline{RESEARCH GRANTS AND CONTRACTS}}

%----------------------------------------------------------------------------------------

\vspace{0.2in} % Some whitespace between sections



\sl{Cardiff \& Vale University Health Board}\\
Operational Research Modelling to Support Cardiff and Vale UHB\\
\pounds 371,427 \hfill{2013-2018}


\sl{EPSRC}\\
Identifying and modelling victim, business regulatory and malware behaviours in a changing cyberthreat landscape\\
\pounds101,659\hfill{2013-2016}


\sl{Aneurin Bevan Health Board}\\
Creation of a Mathematical/OR Modelling Unit to Support the Aneurin Bevan Health Board\\
\pounds319,944 \hfill{2013-2015}


\sl{ESRC}\\
Hate speech? Understanding the modelling of social media identity formation and behaviour through the Cardiff Online Social Media Observatory (COSMOS)\\
\pounds7,015\hfill{2013-2016}


\sl{Health Foundation and Cardiff \& Vale University Health Board}\\
Estimating quality improvement and cost reduction for the patient and local health economy of transferring ENT/audiology services into a community setting\\
\pounds61,237\hfill{2013-2014}


\sl{LANCS (EPSRC)}\\
Post-Doctoral Training Scheme Grant: Investigating the Effects of Individual Behaviour on Hierarchical queueing Systems\\
\pounds5,000\hfill{2012}


\sl{Cardiff University CUROP Award}\\
Developing and Evaluating Mathematical Teaching Resources through Open Source Software\\
\pounds2,200\hfill{2012}

\sl{LANCS (EPSRC)}\\
Post-Doctoral Training Scheme Grant: Choice and Healthcare Investigation Project\\
\pounds2,500\hfill{2010-2011}

\sl{Cardiff University CUROP Award}\\
Patient Choice: A Discrete Event Simulation\\
\pounds2,500\hfill{2010}


\end{resume}
\end{document}
